---
title: "GENETIC.INTERACTION.NETWORK"
author: "Connor O'Meara"
date: "1/24/2020"
output: html_document
---
```{r message=FALSE, warning=FALSE, include=FALSE}
#Load packages into library
library(readxl)
library(matrixStats)
library(stringr)
library(dplyr)
library(lattice)
library(gplots)
library(ggplot2)
library(ggrepel)
library(plyr)
library(tidyverse)
library(gridExtra)
library(pwr)
library(igraph)
library(reshape)
library(pvclust)
library(caret)
library(dslabs)
library(parallel)
library(stabs)
library(splines)
library(foreach)
library(kohonen)
library(MASS)
library(gam)
library(gridExtra)
library(ggfortify)
library(corrplot)
#IMPORT PATHWAY ANNOTATION FILE
NODE_PATHWAY_ANNO <- read.delim("NODE_PATHWAY_ANNO", stringsAsFactors = FALSE)
```

###################################################################################################
# IMPORT RAW DATA AND DATA PREPROCESSING
###################################################################################################

### 1. FROM rag/ghrh values for WT, MUT1, MUT2 and double mutant (DB.MUT) for each pairwise gene interaction experiment,
### 2. USE the Product/Multiplicative method to predict the expected DB.MUT rag/ghrh value for each experiment and compare to observed DB.MUT rag/ghrh value, to
### 3. GET effect size of geneteic interaction (log2 fold-change), genetic interaction type (positive, negative and non-interactive) and significance of interaction.

```{r echo=TRUE, fig.align='center', fig.height=6, fig.keep='all', fig.width=10, message=FALSE, warning=FALSE, results='hide'}
#CREATE LIST OF FILES WITHIN WORKING DIRECTORY, INCLUDING SUBFOLDERS
  list.raw<- list.files(pattern=".xlsx", recursive = TRUE) 

#READ DATA FROM EACH FILE USING LIST OF DATA FILES
  data.raw<- as.vector(lapply(list.raw, read_excel, range="A1:D25", col_names=TRUE, col_types = c("numeric", "numeric", "numeric", "numeric"))) 

#REMOVE "0" VALUE BY ADDING 0.00001 TO ALL VALUES
    data.raw<-lapply(data.raw,function(X)X+0.00001)

#RENAME COLUMN NAMES
  col.names<-c("WT", "MUT1", "MUT2", "DB.MUT")
  for (X in 1:length(data.raw))colnames(data.raw[[X]]) = col.names

#CALCULATE FITNESS OF SINGLE MUTANTS AND DOUBLE MUTANTS RELATIVE TO WT
  GI.list<-lapply(data.raw, function(X)cbind(X, means=t(apply(X, 1, function(Y)Y/colMeans(X[,1, drop=FALSE],na.rm = TRUE)))))

#RENAME LISTS WITH FILE NAMES
  names(GI.list)<-list.raw

#CALCULATE NUMBER OF NA'S FOR EACH LIST
  subset.GI.list<-lapply(1:length(GI.list), function(X)apply(GI.list[[X]][4],2,function(Y)sum(is.na(Y))))

#RETAIN LISTS WITH AT LEAST 3 DATA POINTS 
  GI.list<-GI.list[as.vector(do.call(rbind,lapply(subset.GI.list, function(X)X<23)))] 

#COUNT THE NUMBER OF FISH USED IN EACH EXPERIMENT
  GI.list<-lapply(GI.list, function(X)cbind(X, n.WT=colSums(!is.na(X))[1], row.names = NULL))
  GI.list<-lapply(GI.list, function(X)cbind(X, n.MUT1=colSums(!is.na(X))[2], row.names = NULL))
  GI.list<-lapply(GI.list, function(X)cbind(X, n.MUT2=colSums(!is.na(X))[3], row.names = NULL))
  GI.list<-lapply(GI.list, function(X)cbind(X, n.DB.MUT=colSums(!is.na(X))[4], row.names = NULL))

#PERFORM T.TEST ON SINGLE MUTANTS AND DOUBLE MUTANTS RELATIVE TO WT, AND DOUBLE MUTANT RELATIVE TO LEAST 
  list.names<-names(GI.list)

#CALCULATE SD FOR EACH GROUP
  GI.list<-lapply(GI.list, function(X)cbind(X, SD.WT=sd(X$means.WT, na.rm = TRUE)))
  GI.list<-lapply(GI.list, function(X)cbind(X, SD.MUT1=sd(X$means.MUT1, na.rm = TRUE)))
  GI.list<-lapply(GI.list, function(X)cbind(X, SD.MUT2=sd(X$means.MUT2, na.rm = TRUE)))
  GI.list<-lapply(GI.list, function(X)cbind(X, SD.DB.MUT=sd(X$means.DB.MUT, na.rm = TRUE)))

#CALCULATE MEANS FOR EACH GROUP
  GI.list.means<-lapply(GI.list,function(X)colMeans(X, na.rm = TRUE))

#BIND ALL EXPERIMENTS TOGETHER
  GI.df<-as.data.frame(do.call(rbind, GI.list.means))

#REMOVE EXPERIMENTS IN WHICH MUTANT ARE NO LESS THAN WT
  GI.df<-GI.df[GI.df$means.MUT1<1 & GI.df$means.MUT2<1,]

#ADD FILE NAME TO EACH ROW IT REPRESENTS
  GI.df<-data.frame(FILE=rownames(GI.df), GI.df)

#ASSIGNMENT EXPERIMENT TYPE BY EXTRACTING FOLDER NAME
  for(i in 1:nrow(GI.df)){
  GI.df$EXP.type[i]<-str_split_fixed(GI.df$FILE[i],"[/.]",2)[,1]
  }   

#SORT NODE NAMES ALPHABETICALLY
  GI.df<-cbind.data.frame(NODE1.2=gsub(".*GI\\s*|.xlsx.*", "", rownames(GI.df)),GI.df)
  node.names<-data.frame(NODE1=str_split_fixed(GI.df$NODE1.2, "\\+", 2)[,1], NODE2=str_split_fixed(GI.df$NODE1.2, "\\+", 2)[,2],stringsAsFactors = F)
  node.names<-data.frame(apply(node.names,2,function(X)gsub(X,pattern = " ", replacement = "")),stringsAsFactors = F)
  node.names<-do.call(rbind,apply(t(apply(node.names,1,sort)),1,function(X)data.frame(NODE1=X[1],NODE2=X[2])))
  GI.df<-cbind.data.frame(FILE=GI.df[,2],node.names, EXP.type=GI.df$EXP.type, GI.df[,3:(ncol(GI.df)-1)])
  
#REMOVE SPACES FROM NODE NAMES (IF ANY)
  GI.df$NODE1<-toupper(gsub(" ", "", GI.df$NODE1))
  GI.df$NODE2<-toupper(gsub(" ", "", GI.df$NODE2))

#CONVERT NODE INFORMATION TO CHARACTERS
  GI.df[,1:4]<-apply(GI.df[,1:4],2, as.character)

#COMBINE REPEATED EXPERIMENTS
  GI.df.mean<-aggregate(.~NODE1+NODE2+EXP.type, GI.df[,-1], mean,na.action=na.omit)
  GI.df.sum<-aggregate(.~NODE1+NODE2+EXP.type, GI.df[,-1],sum,na.action=na.omit)
  GI.df.mean[,colnames(GI.df.mean) %in% c("n.WT", "n.MUT1", "n.MUT2", "n.DB.MUT")]<-GI.df.sum[,colnames(GI.df.sum) %in% c("n.WT", "n.MUT1", "n.MUT2", "n.DB.MUT")]

#CONCATENATE FILE NAMES FOR COMBINED DATASETS
GI.df.lab<-aggregate(data=GI.df[,1:4],.~NODE1+NODE2+EXP.type,FUN=paste,collapse=" , ")

#JOIN DATA
  GI.df<-full_join(GI.df.lab,GI.df.mean,by=c("NODE1", "NODE2", "EXP.type"))
  GI.df<-GI.df[complete.cases(GI.df),]

#CALCULATE THE EXPECTED FITNESS OF THE DOUBLE MUTANT (MULTIPLICATIVE METHOD)
  GI.df$PRODUCT<-GI.df$means.MUT1*GI.df$means.MUT2

#CALCULATE LOG2 FOLD-CHANGE BETWEEN OBSERVED (MEANS.DB.MUT) AND EXPECTED FITNESS (PRODUCT)
  GI.df$PRODUCT.log2.FC<-log2(GI.df$means.DB.MUT)-log2(GI.df$PRODUCT)

#CALCULATE ERROR FOR EXPECTED FITNESS BY PROPAGATING ERROR FROM WT AND SINGLE MUTANTS
  GI.df$Prop.SD<-GI.df$PRODUCT * sqrt((GI.df$SD.MUT1/GI.df$means.MUT1)^2 + 
                                            (GI.df$SD.MUT2/GI.df$means.MUT2)^2)
#CALCULATE T STATISTIC BETWEEN EXPECTED AND OBSERVED DB.MUT USING MEAN, SD, N
 t.test2 <- function(m1,m2,s1,s2,n1,n2,m0=0,equal.variance=FALSE)
{
    if( equal.variance==FALSE ) 
    {
        se <- sqrt( (s1^2/n1) + (s2^2/n2) )
        # welch-satterthwaite df
        df <- ( (s1^2/n1 + s2^2/n2)^2 )/( (s1^2/n1)^2/(n1-1) + (s2^2/n2)^2/(n2-1) )
    } else
    {
        # pooled standard deviation, scaled by the sample sizes
        se <- sqrt( (1/n1 + 1/n2) * ((n1-1)*s1^2 + (n2-1)*s2^2)/(n1+n2-2) ) 
        df <- n1+n2-2
    }      
    t <- (m1-m2-m0)/se 
    dat <- c(m1-m2, se, t, 2*pt(-abs(t),df))    
    names(dat) <- c("Difference of means", "Std Error", "t", "p-value")
    return(dat) 
 } 

#CALCULATE SIGNIFICANCE BETWEEN OBSERVED AND EXPECTED DB.MUT RAG1/GHRH VALUES
 ttest<-list()
for(i in 1:nrow(GI.df)){
  ttest[[i]]<-t.test2(m1 = GI.df$means.DB.MUT[i],
          m2 = GI.df$PRODUCT[i], 
          s1 = GI.df$SD.DB.MUT[i],
          s2 = GI.df$Prop.SD[i],
          n1 = GI.df$n.DB.MUT[i],
          n2 = sum(GI.df$n.MUT1[i],GI.df$n.MUT2[i]),
          equal.variance=FALSE)
}
  GI.df<-cbind.data.frame(GI.df, do.call(rbind,ttest)[,3:4])

#DEFINE GENETIC INTERACTION TYPE
  GI.df$GI.type<-NA

#INTERACTION TYPE (MULTIPLICATIVE MODEL)
    for (X in 1:nrow(GI.df))GI.df$GI.type[X] = if(GI.df$PRODUCT.log2.FC[X]>0 & #positive
             GI.df$`p-value`[X]<=0.1 & # significant
             GI.df$means.DB.MUT[X]>(GI.df$PRODUCT[X])+(GI.df$Prop.SD[X]) & #outside error of expected fitness
             GI.df$means.DB.MUT[X]>((min(GI.df$means.MUT1[X],GI.df$means.MUT2[X])+(c(GI.df$SD.MUT1[X],GI.df$SD.MUT2[X])[which.min(c(GI.df$means.MUT1[X],GI.df$means.MUT2[X]))])))) {# greater than least fit mutant
    print("POSITIVE - SUPPRESSIVE")
    } else if (GI.df$PRODUCT.log2.FC[X]>0 &
              GI.df$`p-value`[X]<=0.1 &
              GI.df$means.DB.MUT[X]>(GI.df$PRODUCT[X])+(GI.df$Prop.SD[X]) & #outside error of expected fitness
             GI.df$means.DB.MUT[X]<((min(GI.df$means.MUT1[X],GI.df$means.MUT2[X])+(c(GI.df$SD.MUT1[X],GI.df$SD.MUT2[X])[which.min(c(GI.df$means.MUT1[X],GI.df$means.MUT2[X]))]))))  {
      print("POSITIVE - COEQUAL")
  } else if (GI.df$PRODUCT.log2.FC[X]<0 & 
             GI.df$`p-value`[X]<=0.1 &
             GI.df$means.DB.MUT[X]<(GI.df$PRODUCT[X])-(GI.df$Prop.SD[X])) {
      print("NEGATIVE")
    } else print("NON-INTERACTIVE")
  
  GI.df$NODE1<-gsub(x = GI.df$NODE1, pattern = ".*5FL.*|.*5-FL.*",replacement = "5FU")
  GI.df$NODE2<-gsub(x = GI.df$NODE2, pattern = ".*5FL.*|.*5-FL.*",replacement = "5FU")

#APPEND PATHWAY INFORMATION TO EACH NODE
  matched.df<-data.frame(FILE=GI.df$FILE, NODE1=GI.df$NODE1, PATHWAY1=NODE_PATHWAY_ANNO$PATHWAY[match(GI.df$NODE1, NODE_PATHWAY_ANNO$NODE1)], NODE2=GI.df$NODE2, PATHWAY2=NODE_PATHWAY_ANNO$PATHWAY[match(GI.df$NODE2, NODE_PATHWAY_ANNO$NODE1)],stringsAsFactors = F)

#COLUMN FOR CONCATENATED NODES AND PATHWAYS
  matched.df$NODES<-apply(t(apply(matched.df[,colnames(matched.df) %in% c("NODE1", "NODE2")],1,sort)),1,function(X)paste(X[1],X[2],sep = "_"))
 matched.df$PATHWAYS<- apply(t(apply(matched.df[,colnames(matched.df) %in% c("PATHWAY1", "PATHWAY2")],1,sort)),1,function(X)paste(X[1],X[2],sep = "_"))
  matched.df<-as.data.frame(apply(matched.df,2, as.character))

#CONVERT NODE AND PATHWAY INFORMATION TO CHARACTERS
  GI.df<-left_join(matched.df,GI.df,by=c("FILE", "NODE1", "NODE2"))
  GI.df[,1:8]<-as.data.frame(apply(GI.df[,1:8],2,as.character),stringsAsFactors = FALSE)
```

###################################################################################################
# PLOT GENETIC INTERACTION PROPORTION AND FREQUENCY BY NODES AND PATHWAYS
###################################################################################################

### 1. FROM genetic.interaction.data in the Annotation_files folder generated above,
### 2. USE base R and fisher's exact test, to
### 3. GET proportion and frequency of genetic interaction for individual nodes, pathways and between pathways and determine which are signficant.

```{r echo=TRUE, fig.align='center', fig.height=6, fig.keep='all', fig.width=10, message=FALSE, warning=FALSE, results='hide'}

#IMPORT GENETIC INTERACTION DATA.FRAME 
  GI.df <- read.delim("Genetic.interaction.data", stringsAsFactors = FALSE)

#REMOVE MICELLANEOUS PATHWAYS AND AMBIGOUS INHIBITORS
  GI.df<-GI.df %>%
    filter(PATHWAY1!="MISCELLANEOUS", PATHWAY2!="MISCELLANEOUS", NODE1!="SAHA", NODE2!="SAHA")

#ENSURE DATA IS REPRESENTED FOR EACH NODE
  GI.df.2<-GI.df %>%
    dplyr::select(NODE1, NODE2, PATHWAYS, GI.type)
  GI.df.2<-rbind(GI.df.2,data.frame(NODE1=GI.df.2$NODE2, NODE2=GI.df.2$NODE1, PATHWAYS=GI.df.2$PATHWAYS, GI.type=GI.df.2$GI.type))

#INDIVIDUAL NODES
    #PLOT PROPORTIONS
    plot.order<-unique(NODE_PATHWAY_ANNO$NODE1[order(NODE_PATHWAY_ANNO$PATHWAY, decreasing = F)])
    plot.order<-plot.order[plot.order %in% GI.df.2$NODE1]
    INT.p<-prop.table(table(GI.df.2$NODE1,GI.df.2$GI.type),1)
    barplot(as.matrix(t(INT.p[match(plot.order,(rownames(INT.p))),])), 
            las=2, 
            cex.names = 0.6, 
            col = c("deeppink", "black", "darkslategray1", "deepskyblue"),
            main = "Interaction - Proportion") 
    legend("left", 
           legend = c("POSITIVE - SUPPRESSIVE", "POSITIVE - COEQUAL", "NON-INTERACTIVE", "NEGATIVE"), 
           fill = c("deepskyblue", "lightcyan", "black", "deeppink"),
           horiz = F, inset = c(1,0), xpd = TRUE)

  #PLOT FREQUENCY
    INT.f<-table(GI.df.2$NODE1,GI.df.2$GI.type)
    barplot(as.matrix(t(INT.f[match(plot.order,(rownames(INT.f))),])), 
            las=2, 
            ylim = c(0,35),
            cex.names = 0.6, 
            col = c("deeppink", "black", "lightcyan", "deepskyblue"),
            main = "Interaction - Frequency"
    ) 
    nodes<-unique(c(GI.df$NODE1, GI.df$NODE2))
  
  #NON-PARAMETRIC TEST FOR SIGNFICANCE
    fishers.df<-matrix(ncol = 4,data = t(INT.f), byrow = T)
    colnames(fishers.df)<-c("NEGATIVE", "NON-INTERACTIVE", "POSITIVE - COEQUAL", "POSITIVE - SUPPRESSIVE")
    rownames(fishers.df)<-rownames(INT.f)
    fishers.df<-as.data.frame(fishers.df)
    fishers.df$POSITIVE<-rowSums(fishers.df[,3:4])
    fishers.df<-fishers.df[,-c(3:4)]
    fishers.df$Fishers.t.test<-sapply(1:nrow(fishers.df),function(X) fisher.test(rbind(fishers.df[X,], colSums(fishers.df)))$p.value)
        fishers.df<-fishers.df[order(fishers.df$Fishers.t.test,decreasing = F),]
    fishers.df<-rbind(fishers.df,colSums(fishers.df))
    rownames(fishers.df)[nrow(fishers.df)]<-"Total"
    fishers.df[nrow(fishers.df), ncol(fishers.df)]<-1
    fishers.df$BH.corrected<-p.adjust(fishers.df$Fishers.t.test, method = "BH")
    tab1<-fishers.df

#INDIVIDUAL PATHWAYS
    #PLOT FREQUENCY
    pathwys<-unique(c(GI.df$PATHWAY1, GI.df$PATHWAY2))
     mt.by.pathway<-list()
    for(i in 1:length(pathwys)){
      mt.by.pathway[[i]]<-table(GI.df$GI.type[which(grepl(x = GI.df$PATHWAYS, pattern = pathwys[i])==TRUE)])
    }
    mt.by.pathway<-do.call(bind_rows,mt.by.pathway)
    mt.by.pathway[is.na(mt.by.pathway)]<-0
    rownames(mt.by.pathway)<-pathwys
    par(mar=c(8,5,5,0))
    barplot(t(mt.by.pathway), 
            las=2, 
            ylim = c(0,150),
            cex.names = 0.6, 
            col = c("deeppink", "black", "lightcyan", "deepskyblue"),
            main = "Interaction - Frequency"
    ) 
    mt.by.pathway<-as.data.frame(mt.by.pathway)
    mt.by.pathway$POSITIVE<-rowSums(mt.by.pathway[,3:4])
    mt.by.pathway<-mt.by.pathway[,-c(3:4)]
  
  #NON-PARAMETRIC TEST FOR SIGNFICANCE
    mt.by.pathway$Fishers.t.test<-sapply(1:nrow(mt.by.pathway),function(X) X = fisher.test(rbind(mt.by.pathway[X,], colSums(mt.by.pathway)))$p.value)
    mt.by.pathway<-mt.by.pathway[order(mt.by.pathway$Fishers.t.test,decreasing = F),]
    mt.by.pathway$BH.corrected<-p.adjust(mt.by.pathway$Fishers.t.test, method = "BH")
    tab2<-mt.by.pathway
    mt.by.pathway<-list()
  
  #PLOT PROPORTIONS
    for(i in 1:length(pathwys)){
      mt.by.pathway[[i]]<-prop.table(table(GI.df$GI.type[which(grepl(x = GI.df$PATHWAYS, pattern = pathwys[i])==TRUE)]))
    }
    mt.by.pathway<-do.call(bind_rows,mt.by.pathway)
    mt.by.pathway[is.na(mt.by.pathway)]<-0
    rownames(mt.by.pathway)<-pathwys
    par(mar=c(8,5,5,0))
    barplot(t(mt.by.pathway), 
            las=2, 
            ylim = c(0,1),
            cex.names = 0.6, 
            col = c("deeppink", "black", "lightcyan", "deepskyblue"),
            main = "Interaction - Proportion"
    ) 
#COMBINED PATHWAY    
  #PLOT FREQUENCY   
    INT.f<-table(GI.df$PATHWAYS,GI.df$GI.type)
    par(mar=c(8,5,5,0))
    barplot(as.matrix(t(INT.f[order(rowSums(INT.f), decreasing = T),])), 
          las=2, 
         ylim = c(0,40),
          cex.names = 0.6, 
          col = c("deeppink", "black", "lightcyan", "deepskyblue"),
          main = "Interaction - Proportion") 
  
  #PLOT PROPORTIONS   
    INT.p<-prop.table(table(GI.df$PATHWAYS,GI.df$GI.type),1)
    par(mar=c(8,5,5,0))
    barplot(as.matrix(t(INT.p[order(rowSums(INT.f), decreasing = T),])), 
          las=2, 
          cex.names = 0.6, 
          col = c("deeppink", "black", "lightcyan", "deepskyblue"),
          main = "Interaction - Proportion") 
  
  #NON-PARAMETRIC TEST FOR SIGNFICANCE
    fishers.df<-matrix(ncol = 4,data = t(INT.f), byrow = T)
    colnames(fishers.df)<-c("NEGATIVE", "NON-INTERACTIVE", "POSITIVE - COEQUAL", "POSITIVE - SUPPRESSIVE")
    rownames(fishers.df)<-rownames(INT.p)
    fishers.df<-as.data.frame(fishers.df)
    fishers.df$POSITIVE<-rowSums(fishers.df[,3:4])
    fishers.df<-fishers.df[,-c(3:4)]
    fishers.df$Fishers.t.test<-sapply(1:nrow(fishers.df),function(X) fisher.test(rbind(fishers.df[X,], colSums(fishers.df)))$p.value)
    fishers.df<-fishers.df[order(fishers.df$Fishers.t.test,decreasing = F),]
    fishers.df<-rbind(fishers.df,colSums(fishers.df))
    rownames(fishers.df)[nrow(fishers.df)]<-"Total"
    fishers.df[nrow(fishers.df), ncol(fishers.df)]<-1
        fishers.df$BH.corrected<-p.adjust(fishers.df$Fishers.t.test, method = "BH")
        tab3<-fishers.df
```

###################################################################################################
#### PLOT GENETIC INTERACTION NETWORK (ALL INTERACTIONS)
###################################################################################################

### 1. FROM genetic.interaction.data in the Annotation_files folder generated above,
### 2. USE igraphs, to
### 3. GET plots of genetic interactions between nodes, grouping by biological pathway.

```{r, message=FALSE, warning=FALSE, results='hide',fig.keep='all', echo=TRUE,fig.height = 12,fig.width = 12,fig.align='center'}

#REMOVE MICELLANEOUS PATHWAYS AND AMBIGOUS INHIBITORS
  NODE_PATHWAY_ANNO<-NODE_PATHWAY_ANNO[NODE_PATHWAY_ANNO$PATHWAY!="MISCELLANEOUS" & NODE_PATHWAY_ANNO$NODE1!="CCT5" & NODE_PATHWAY_ANNO$NODE1!="PNRC1" & NODE_PATHWAY_ANNO$NODE1!="AMX" & NODE_PATHWAY_ANNO$NODE1!="SAHA" & NODE_PATHWAY_ANNO$NODE1!="HOMO",]  
  NODE_PATHWAY_ANNO<-NODE_PATHWAY_ANNO %>%
    filter(!NODE1 %in% c("CCT5", "AMX", "SAHA", "HOMO"))

#DEFINE EDGE AND NODE ATTRIBUTE
  V<- NODE_PATHWAY_ANNO
  E<- GI.df %>% dplyr::select(NODE1,NODE2,PATHWAY1, PATHWAY2, PRODUCT.log2.FC, GI.type, EXP.type) %>% filter(PRODUCT.log2.FC!="-Inf", NODE1!="CCT5", NODE1 %in% NODE_PATHWAY_ANNO$NODE1, NODE2 %in% NODE_PATHWAY_ANNO$NODE1 )
    E$GI.type[grepl(E$GI.type,pattern = "POSITIVE.*")]<-"POSITIVE"

#CREATE NETWORK
    net<- graph.data.frame(d=E, vertices=V, directed=FALSE)

#CREATE COLOUR VECTORS FOR EDGES AND NODES
    edge.col<- c("deeppink","black","deepskyblue")
    node.col<- c("deeppink3","firebrick1","darkorange","mediumseagreen", "cornflowerblue","slategray1","gold")
     
#GROUP NODES BY GO TERM
  V(net)$Group1 = node.col[as.factor(NODE_PATHWAY_ANNO$PATHWAY)]

#CREATE X Y COORDINATES FOR PREFERRED LAYOUT IN IGRAPH
  ER<-NODE_PATHWAY_ANNO$NODE1[NODE_PATHWAY_ANNO$PATHWAY=="ER"]
  DNA<-NODE_PATHWAY_ANNO$NODE1[NODE_PATHWAY_ANNO$PATHWAY=="DNA"]
  SPLICE<-NODE_PATHWAY_ANNO$NODE1[NODE_PATHWAY_ANNO$PATHWAY=="MRNA PROCESSING"]
  CELL<-NODE_PATHWAY_ANNO$NODE1[NODE_PATHWAY_ANNO$PATHWAY=="CHR.SEG"]
  RIBO<-NODE_PATHWAY_ANNO$NODE1[NODE_PATHWAY_ANNO$PATHWAY=="RIBOSOME"]
  IMMUNE<-NODE_PATHWAY_ANNO$NODE1[NODE_PATHWAY_ANNO$PATHWAY=="IMMUNE"]
  PIP<-NODE_PATHWAY_ANNO$NODE1[NODE_PATHWAY_ANNO$PATHWAY=="PIP"]

#CREATE A PREFERRED CIRCULAR LAYOUT FOR EACH PATHWAY GROUP, MULTIPLED BY SCALAR TO CHANGE DIAMETER OF PATHWAY NODE
  lay.list=list(
    ER.lay <- layout_in_circle(induced_subgraph(net, V(net)$name %in% ER))*3.3,
    RIBO.lay <- layout_in_circle(induced_subgraph(net, V(net)$name %in% RIBO))*1.65,
    SPLICE.lay <-layout_in_circle(induced_subgraph(net,V(net)$name %in% SPLICE))*4.3,
    CELL.lay <- layout_in_circle(induced_subgraph(net, V(net)$name %in% CELL))*2, 
    IMMUNE.lay <- layout_in_circle(induced_subgraph(net, V(net)$name %in% IMMUNE))*3.9,
    PIP.lay <- layout_in_circle(induced_subgraph(net, V(net)$name %in% PIP))*1.5,  
    DNA.lay <- layout_in_circle(induced_subgraph(net, V(net)$name %in% DNA))*4.8
   )
  l<-rbind(ER.lay,RIBO.lay,SPLICE.lay,CELL.lay,IMMUNE.lay,PIP.lay,DNA.lay)
  l.names<-c(ER,RIBO ,SPLICE,CELL,IMMUNE,PIP,DNA)
  l = do.call(rbind,lay.list)
  l =do.call(rbind,lapply(1:7,function(i)cbind(lay.list[[i]][,1]+13*cos(((1:7)*2*pi/7))[[i]],lay.list[[i]][,2]+13*sin(((1:7)*2*pi/7))[[i]])))
  l = l[order(match(l.names,V$NODE1)),]

#PLOT NETWORKS PARTITIONED BY BY GENETIC INTERACTION TYPE
  par(mar=c(1,1,1,1))
#PLOT ALL GENETIC INTERACTIONS
  plot(net,
        vertex.shape="circle",
        vertex.size=15,	
      vertex.label.color= "black",
        vertex.label.font	=2,
       vertex.label.cex=0.6,
       vertex.label.color="#000000",
        edge.curved=0, 
        vertex.frame.color="#000000", 
        edge.color=edge.col[as.factor(E(net)$GI.type)], 
        vertex.label.cex=.7, 
        edge.width=abs(E(net)$PRODUCT.log2.FC),
        vertex.color=V(net)$Group1, 
        layout=l)

#PLOT NEGATIVE INTERACTIONS
  net.neg<-delete_edges(net, E(net)[E(net)$GI.type!="NEGATIVE"])
  plot(net.neg,
        vertex.shape="circle",
        vertex.size=15,	
      vertex.label.color= "black",
        vertex.label.font	=2,
       vertex.label.cex=0.6,
        edge.curved=0, 
        vertex.frame.color="#555555", 
        edge.color=edge.col[-c(2,3,4)][as.factor(E(net.neg)$GI.type)], 
        vertex.label.cex=.7, 
        edge.width=abs(E(net.neg)$PRODUCT.log2.FC),
        vertex.color=V(net.neg)$Group1, 
        layout=l)
#PLOT POSITIVE INTERACTION (SUPPRESSIVE AND COEQUAL)
  net.pos<-delete_edges(net, E(net)[E(net)$GI.type=="NEGATIVE"])
  net.pos<-delete_edges(net.pos, E(net.pos)[E(net.pos)$GI.type=="NON-INTERACTIVE"])
  plot(net.pos,
        vertex.shape="circle",
        vertex.size=15,	
       vertex.label.color= "black",
        vertex.label.font	=2,
       vertex.label.cex=0.6,
        edge.curved=0, 
        vertex.frame.color="#555555", 
        edge.color=edge.col[-c(1,2)][as.factor(E(net.pos)$GI.type)], 
        vertex.label.cex=.7, 
        edge.width=abs(E(net.pos)$PRODUCT.log2.FC),
        vertex.color=V(net.pos)$Group1, 
        layout=l)
#PLOT NON-INTERACTIVE
  net.n.i<-delete_edges(net, E(net)[E(net)$GI.type=="NEGATIVE"])
  net.n.i<-delete_edges(net.n.i, E(net.n.i)[E(net.n.i)$GI.type=="POSITIVE - SUPPRESSIVE"])
  net.n.i<-delete_edges(net.n.i, E(net.n.i)[E(net.n.i)$GI.type=="POSITIVE - COEQUAL"])
  plot(net.n.i,
        vertex.shape="circle",
        vertex.size=15,	
        vertex.label.font	=2,
      vertex.label.color= "black",
       vertex.label.cex=0.6,
        edge.curved=0, 
        vertex.frame.color="#555555", 
        edge.color=edge.col[-c(1,3,4)][as.factor(E(net.n.i)$GI.type)], 
        vertex.label.cex=.7, 
        edge.width=abs(E(net.n.i)$PRODUCT.log2.FC),
        vertex.color=V(net.n.i)$Group1, 
        layout=l)
```

###################################################################################################
#### PLOT GENETIC INTERACTION NETWORK (PROPORTION BETWEEN PATHWAYS)
###################################################################################################

### 1. FROM genetic.interaction.data in the Annotation_files folder generated above,
### 2. USE table and igraphs, to
### 3. GET plots of genetic interactions proportions between nodes, grouping by biological pathway.

```{r echo=TRUE, fig.align='center', fig.height=10, fig.keep='all', fig.width=10, message=FALSE, warning=FALSE, results='hide'}

#GROUP COEQUAL AND SUPPRESSIVE INTERACTION INTO A SINGLE POSITIVE GROUP
  GI.df.2<-GI.df %>% filter(PRODUCT.log2.FC!="-Inf", )
  GI.df.2$GI.type<-gsub("POSITIVE - COEQUAL|POSITIVE - SUPPRESSIVE", "POSITIVE",x = GI.df.2$GI.type)

#CREATE TABLE OF GENETIC INTERACTION TYPES PROPORTIONS BETWEEN PATHWAYS
  INT.p<-prop.table(table(GI.df.2$PATHWAYS,GI.df.2$GI.type),1)
  x<-as.data.frame(INT.p)
  y<-cbind.data.frame(str_split(x$Var1, "_", simplify = T),x)
  colnames(y)<-c("PATHWAY1", "PATHWAY2", "PATHWAYS", "GI.type", "PROP")

#DEFINE EDGE AND NODE ATTRIBUTE
  V<- unique(c(as.character(y$PATHWAY1), as.character(y$PATHWAY2)))      
  E<- y 

#CREATE NETWORK
  net.path<- graph.data.frame(d=E, vertices=V, directed=FALSE)

#CREATE A PREFERRED CIRCULAR LAYOUT FOR EACH PATHWAY GROUP, MULTIPLED BY SCALAR TO CHANGE DIAMETER OF PATHWAY NODE
  lay.list=list(
    ER.lay <- layout_in_circle(induced_subgraph(net.path, V(net.path)$name == "ER")),
    RIBO.lay <- layout_in_circle(induced_subgraph(net.path, V(net.path)$name == "RIBOSOME")),
    SPLICE.lay <-layout_in_circle(induced_subgraph(net.path,V(net.path)$name == "MRNA PROCESSING")),
    CELL.lay <- layout_in_circle(induced_subgraph(net.path, V(net.path)$name == "CHR.SEG")),
    PIP.lay <- layout_in_circle(induced_subgraph(net.path, V(net.path)$name == "PIP")),
    IMMUNE.lay <- layout_in_circle(induced_subgraph(net.path, V(net.path)$name == "IMMUNE")),
    DNA.lay <- layout_in_circle(induced_subgraph(net.path, V(net.path)$name == "DNA"))
  )
  l<-rbind(ER.lay,RIBO.lay,SPLICE.lay,CELL.lay,IMMUNE.lay,PIP.lay ,DNA.lay)
  l.names<-c("ER","RIBOSOME" ,"MRNA PROCESSING","CHR.SEG", "IMMUNE","PIP","DNA")
  l =do.call(rbind,lapply(1:7,function(i)cbind(lay.list[[i]][,1]+13*cos(((1:7)*2*pi/7))[[i]],lay.list[[i]][,2]+13*sin(((1:7)*2*pi/7))[[i]])))
  l = l[order(match(l.names,E$PATHWAY1)),]

#CREATE COLOUR VECTORS FOR EDGES AND LINE CURVITURE VECTORS
  edge.col.cor<- c("deeppink", "black", "deepskyblue")
  curve.vec<-c(-0.1,0,0.1)

#LABEL EDGE IT PROPORTION IS 40% OR GREATER
  x<-round(E(net.path)$PROP,1)
  x[x<0.4]<-NA
#PLOT ALL GENETIC INTERACTIONS BY PROPORTIONS
  plot(net.path,
       vertex.shape="circle",
       vertex.size=c(5,10.1,7,5,7,4.5,4.5)*9.5,	
       vertex.label.font	=2,
       vertex.label.cex=0.8,
       edge.curved=curve.vec[as.factor(E(net.path)$GI.type)], 
       vertex.frame.color=node.col, 
       edge.color=edge.col.cor[as.factor(E(net.path)$GI.type)], 
       edge.width=(abs(E(net.path)$PROP)+0.0001)*5,
       vertex.color=adjustcolor(node.col,0.05), 
       edge.label.color="black",
       edge.label.cex=1,
       layout=l)
```

###################################################################################################
#### BETWEEN PATHWAY INTERACTION ENRICHMENT, P VALUE BY BOOTSTRAPPING
###################################################################################################

### 1. FROM proportion of genetic interaction in the network,
### 2. USE Monte Carlo simmulation, to
### 3. GET probabilities of observed proportion of interactions .

```{r}
#DETERMINE PROBABILITY OF EACH GENETIC INTERACTION TYPE
  GI.type.prop<-as.numeric(prop.table(table(GI.df$GI.type)))
  GI.type.prop<-c(GI.type.prop[1:2], sum(GI.type.prop[3:4]))
  GI.type.vec<-c("NEGATIVE", "NON-INTERACTIVE","POSITIVE")
  DF<-GI.df[,colnames(GI.df) %in% c("NODE1", "PATHWAY1", "NODE2", "PATHWAY2")]
  x<-as.data.frame(INT.p)

#POSITIVE INTERACTIONS BETWEEN,
  #CHR.SEG and DNA
    vec<-c("CHR.SEG", "DNA")
    CHR.SEG.DNA<-replicate(10000,{
    samp<-sample(GI.type.vec,nrow(DF),prob =  GI.type.prop, replace = TRUE)
    perm.DF<-cbind.data.frame(DF, samp)
    sub.DF<-perm.DF[perm.DF$PATHWAY1 %in% vec & perm.DF$PATHWAY2 %in% vec,]
    sub.DF<-sub.DF[sub.DF$PATHWAY1!=sub.DF$PATHWAY2,]
    prop.table(table(sub.DF$samp=="POSITIVE"))[2]
    })
  #Probability of greater than 23% positive interactions
  paste(vec[1],vec[2], "P_<", length(which(CHR.SEG.DNA>=x$Freq[x$Var2 == "POSITIVE" & x$Var1=="CHR.SEG_DNA"]))/length(CHR.SEG.DNA), sep = "_")

  #CHR.SEG and RIBOSOME
    vec<-c("CHR.SEG", "RIBOSOME")
    CHR.SEG.RIBO<-replicate(10000,{
    samp<-sample(GI.type.vec,nrow(DF),prob =  GI.type.prop, replace = TRUE)
    perm.DF<-cbind.data.frame(DF, samp)
    sub.DF<-perm.DF[perm.DF$PATHWAY1 %in% vec & perm.DF$PATHWAY2 %in% vec,]
    sub.DF<-sub.DF[sub.DF$PATHWAY1!=sub.DF$PATHWAY2,]
    prop.table(table(sub.DF$samp=="POSITIVE"))[2]
    })
    #Probability of greater than 23% positive interactions
    paste(vec[1],vec[2], "P_<", length(which(CHR.SEG.RIBO>=x$Freq[x$Var2 == "POSITIVE" & x$Var1=="CHR.SEG_RIBOSOME"]))/length(CHR.SEG.RIBO), sep = "_")

#NEGATIVE INTERACTIONS BETWEEN,
  #MRNA and ER
    vec5<-c("MRNA PROCESSING", "ER")
    MRNA.ER<-replicate(10000,{
    samp<-sample(GI.type.vec,nrow(DF), prob =  GI.type.prop,replace = TRUE)
    perm.DF<-cbind.data.frame(DF, samp)
    sub.DF<-perm.DF[perm.DF$PATHWAY1 %in% vec5 & perm.DF$PATHWAY2 %in% vec5,]
    sub.DF<-sub.DF[sub.DF$PATHWAY1!=sub.DF$PATHWAY2,]
    prop.table(table(sub.DF$samp=="NEGATIVE"))[2]
    })
    #Probability of greater than 30% positive interactions
    paste(vec5[1],vec5[2], "P_<", length(which(MRNA.ER>=x$Freq[x$Var2 == "NEGATIVE" & x$Var1=="ER_MRNA PROCESSING"]))/length(MRNA.ER),sep = "_")

  #ER and CHR.SEG
    vec6<-c("CHR.SEG", "ER")
    CHR.SEG.ER<-replicate(10000,{
    samp<-sample(GI.type.vec,nrow(DF), prob =  GI.type.prop,replace = TRUE)
    perm.DF<-cbind.data.frame(DF, samp)
    sub.DF<-perm.DF[perm.DF$PATHWAY1 %in% vec6 & perm.DF$PATHWAY2 %in% vec6,]
    sub.DF<-sub.DF[sub.DF$PATHWAY1!=sub.DF$PATHWAY2,]
    prop.table(table(sub.DF$samp=="NEGATIVE"))[2]
    })
    #Probability of greater than 47% positive interactions
    paste(vec6[1],vec6[2], "P_<", length(which(CHR.SEG.ER>=x$Freq[x$Var2 == "NEGATIVE" & x$Var1=="CHR.SEG_ER"]))/length(CHR.SEG.ER),sep = "_")

  #ER and DNA
    vec3<-c("ER", "DNA")
    ER.DNA<-replicate(10000,{
    samp<-sample(GI.type.vec,nrow(DF), prob =  GI.type.prop,replace = TRUE)
    perm.DF<-cbind.data.frame(DF, samp)
    sub.DF<-perm.DF[perm.DF$PATHWAY1 %in% vec3 & perm.DF$PATHWAY2 %in% vec3,]
    sub.DF<-sub.DF[sub.DF$PATHWAY1!=sub.DF$PATHWAY2,]
    prop.table(table(sub.DF$samp=="NEGATIVE"))[2]
    })
    #Probability of greater than 20% positive interactions
    paste(vec3[1],vec3[2], "P_<", length(which(ER.DNA>=x$Freq[x$Var2 == "NEGATIVE" & x$Var1=="DNA_ER"]))/length(ER.DNA),sep = "_")

  #MRNA PROCESSING and DNA
    vec3<-c("MRNA PROCESSING", "DNA")
    MRNA.DNA<-replicate(10000,{
    samp<-sample(GI.type.vec,nrow(DF), prob =  GI.type.prop,replace = TRUE)
    perm.DF<-cbind.data.frame(DF, samp)
    sub.DF<-perm.DF[perm.DF$PATHWAY1 %in% vec3 & perm.DF$PATHWAY2 %in% vec3,]
    sub.DF<-sub.DF[sub.DF$PATHWAY1!=sub.DF$PATHWAY2,]
    prop.table(table(sub.DF$samp=="NEGATIVE"))[2]
    })
    #Probability of greater than 20% positive interactions
    paste(vec3[1],vec3[2], "P_<", length(which(MRNA.DNA>=x$Freq[x$Var2 == "NEGATIVE" & x$Var1=="DNA_MRNA PROCESSING"]))/length(MRNA.DNA),sep = "_")
```